\EVOSUITE at the SBST 2020 Tool Competition

### 2020-04-04 papers/sbst20/main.tex
Update discussion and conclusion

\begin{table*}[t]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the
    SBST benchmark classes.}
\vspace{-1em}
\resizebox{0.8\textwidth}{!}{  
\input{mainTable.tex}
}	
\end{table*}

@@

\subsubsection*{FESCAR-15} According to the \texttt{transcript.csv} file, it
seems that the generated test cases do cover some lines of code but no
branches/conditions.  
%Looking at the \texttt{logs.log}, \EVOSUITE also reported
%0\% coverage and we could not find any issues in any %log file. 
For further investigation, we ran \EVOSUITE as stand-alone tool (i.e., wot using the benchmark infrastructure but it was still not capable of covering any line. Through manual investigation, we notice that the CUT manages objects of the class \texttt{ScheduledExecutorService} and \textit{threads}. Generating tests for CUTs that produce or manage threads is challenging and a well-known open problem in the literature~\cite{FrA13a}.
\textcolor{red}{Annibale: does EvoSuite allow to generate threads within the scope of the generated tests? If I am not mistaken, it does not for security reasons. Should we mention it?
}

@@

\subsubsection*{FESCAR-2} This CUT contains only a few branches (i.e., 14) and lines (i.e., 19). \EVOSUITE could generate test cases that could cover around 20\%-25\% of lines but 0\% of condition coverage. The generated tests cover branchless methods and the root branch of the method \texttt{lookup}, which is the only method with some conditions. It is worth noticing that \EVOSUITE could not complete a single generation, even with a search budget of 180s. The CUT is particularly expensive, and each generated test requires seconds for its execution. Low search budgets are thus not feasible nor recommended for this CUT.

@@

\subsubsection*{GUAVA-110, GUAVA-240} Both classes make use of the annotation \texttt{@Nullable}. GUAVA-110 uses the annotation for the input parameter of the method \texttt{equals(...)}, while GUAVA-240 uses it for the methods \texttt{contains(...)} and \texttt{remove(...)}. The static analyzer implemented in \EVOSUITE does not handle the annotation \texttt{@Nullable} and triggers the error \textit{``Cannot find symbol''}.

@@

\subsubsection*{PDFBOX-157} \EVOSUITE crashed in 9 out ten times with a search budget of 60s, and in 10 out of 10 runs for larger budgets.

@@

\subsubsection*{FESCAR-23, FESCAR-37, FESCAR-7, FESCAR-8, GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285, PDFBOX-40, PDFBOX-91, PDFBOX-62, SPOON-105, SPOON-253} The mutation analysis
failed due to a \texttt{java.util.concurrent.ExecutionException} thrown by the
experimental infrastructure.

@@

\subsubsection*{PDFBOX-235, SPOON-155} \EVOSUITE crashed due to some Mocking stuff.

@@

>>>>

\begin{table*}[t!]
  \centering
  \caption{\label{table:results}Detailed results of \EVOSUITE on the
    SBST benchmark classes.}
%\vspace{-1em}
\resizebox{0.9\textwidth}{!}{  
\input{mainTable.tex}
}	
\end{table*}

Table~\ref{table:results} summarizes the results achieved by \EVOSUITE on the competition classes and search budgets. In general, the performance of \EVOSUITE was in line with previous
results. As usual, there are some noteable cases where \EVOSUITE did not perform well. In the following, we discuss these cases, such that future work can address open problems in automated unit test generation.

@@

\subsubsection*{FESCAR-15} According to the results provided by the competition
organizers, it seems that the generated test cases do cover some lines of code
but no branches/conditions.
%Looking at the \texttt{logs.log}, \EVOSUITE also reported
%0\% coverage and we could not find any issues in any %log file. 
For further investigation, we ran \EVOSUITE as stand-alone tool (i.e., not using the benchmark infrastructure but it was still not capable of covering any line. Through manual investigation, we notice that the CUT manages objects of the class \texttt{ScheduledExecutorService} and \textit{threads}. Generating tests for CUTs that produce or manage threads is challenging and a well-known open problem in the literature~\cite{FrA13a}. \EVOSUITE does not prevent the CUT to spawn new threads, but it (1) forces the use of a wrapper class that leads to deterministic stack traces and thread names, and (2) any spawned threads are joined and removed after a test execution to ensure a clean state for successive test executions, which may consume a substantial amount of time.

@@

\subsubsection*{FESCAR-2} This CUT contains only a few branches (i.e., 14) and lines (i.e., 19). \EVOSUITE was only able to generate test cases that cover around 20\%-25\% of lines but 0\% of condition coverage. The generated tests cover branchless methods and the root branch of the method \texttt{lookup}, which is the only method with some conditions. It is worth noticing that \EVOSUITE could not complete a single generation, even with a search budget of 180s. The CUT is particularly expensive, and each generated test requires seconds for its execution. Low search budgets are thus not feasible nor recommended for this CUT.

@@

\subsubsection*{GUAVA-110, GUAVA-240} Both classes make use of the annotation \texttt{@Nullable}. GUAVA-110 uses the annotation for the input parameter of the method \texttt{equals(...)}, while GUAVA-240 uses it for the methods \texttt{contains(...)} and \texttt{remove(...)}. The static analyzer implemented in \EVOSUITE does not handle the annotation \texttt{@Nullable} and triggers the error \textit{``Cannot find symbol''}. This, in retrospect, would have been easy to avoid.

@@

\subsubsection*{PDFBOX-157} \EVOSUITE crashed in 9 out ten times with a search budget of 60s, and in 10 out of 10 runs for larger budgets. The exact reasons are not yet clear, and will require further debugging.

@@

\subsubsection*{FESCAR-23, FESCAR-37, FESCAR-7, FESCAR-8, GUAVA-212, GUAVA-22,
PDFBOX-265, PDFBOX-278, PDFBOX-285, PDFBOX-40, PDFBOX-91, PDFBOX-62, SPOON-105,
SPOON-253} For all these classes the mutation analysis failed due to a
\texttt{java.util.concurrent.\\ExecutionException} thrown by the experimental
infrastructure, rather than by \EVOSUITE.

@@

\subsubsection*{PDFBOX-235, SPOON-155} In these two cases, \EVOSUITE crashed while attempting to set up mock objects; these are bugs in \EVOSUITE.

@@

This paper reports on the participation of the \EVOSUITE test
generation tool in the 8th SBST Java Unit Testing Tool Contest. With
an overall score of \TOTALPOINTS points, \EVOSUITE achieved the
highest score of all tools in the competition. Despite the many years of development, the benchmark used in the competition points out several opportunities for improvement, which we discussed in this paper.

To learn more about \EVOSUITE, visit our Web site:
\begin{center}
%\url{http://evosuite.org/}
\texttt{http://www.evosuite.org}
\end{center}
